Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline

### 2017-09-13 draft/response_to_referee.txt

-----
# 9. "purity and completeness"

We agree with the referee that the purity and completeness tests are very important for
survey like this, and SynPipe can be a useful tool for this purpose.

At the same time, careful tests for this purpose are beyond the scope of this paper, where
we simply want to demonstrate the application of SynPipe and provide simple photometric
benchmark tests for stars and galaxies.

Following the suggestions from the referee, we modify the text with more discussions on
this, and here are the main points:
    - Section 4.2: We explain that it is beyond the scope of this work to look into this
      carefully.  Detection limits and completeness are normally defined for point sources.  
      As we show using the PSF S/N, it depends on the seeing condition and show spatial 
      changes which requires more careful designs and higher density of fake stars. 
      Detection completeness of point sources for HSC DR1 is investigated in Aihara+2017
      (see Section 5.7) using a different method. 
    - Misclassification is briefly discussed in Section 6.2. The design of our tests and the 
      number density of synthetic galaxies are not perfect to thoroughly test the star-galaxy 
      separation. So our results just demonstrate the capability and briefly discuss the 
      current situation for star/galaxy separation.  We find that, right now, hscPipe tends 
      to provide a very complete sample for galaxy but with considerable fraction of star 
      contamination at the faint end.  In Aihara+2017, the star/galaxy separation issue 
      is discussed in Section 5.7, where they draw the same conclusion using different 
      method. 
    - The current method adopted by hscPipe focuses on the magnitude different between PSF 
      and CModel photometry and is known to have limitations (see Section 4.9.10 of 
      Bosch+2017) and issues (e.g. the one related to the current CModel algorithm; see 
      Appendix 2 in Bosch+2017).  All these conclusions are reflected in our simple test. 
      On the other hand, hscPipe team is working on replacing the star/galaxy separation 
      algorithm with a much improved one (based on extreme deconvolution method, also 
      see Section of 4.9.10 of Bosch+2017).  We will test its performance after the next 
      data release. 
    - We expand the discussion in Section 6.2 to provide more information about star/galaxy 
      separation tests and emphasize the importance of such tests as suggested by the referee.

@@

For stars, first, fraction of stars with such extreme colors are very low.  The
discrepency can barely be noticed on the comparisons of 1-D color distributions. 
We think the likely reasons for this are: 
    - There are still scattered light on the y-band images that are not accounted for.
      This known prolblem can affect the accuracy of y-band photometry and is discussed in 
      Section 5.8.14 in Aihara+2017. 
    - Background level is much higher in z and y-band, and background subtraction could
      suffer from higher uncertainties.  Right now, SynPipe can still not test the impact
      of background subtraction on photometry, and it will be investigated in the future. 
    - We modify text in Section 5.1.3 to breifly explain this.

As for galaxies, the same background and y-band scatter light issues also exist.  However,
the dynamical ranges for i-z and z-y colors are narrower.  Also the CModel color
uncertainties are higher than the PSF ones.  Both of these factors make it harder to spot
discrepencies of color distributions.  However, we still see discrenpencies between the
input and recovered z-y colors. 
    - We expand the discussion in Section 5.2.3 a little to address this issue.

----
7. p.22

The referee is correct that, for highly blended stars, the biases on their PSF colors are 
still quite big.  What we meant here is that the biases for PSF magnitude are much worse 
as the total fluxes of blended stars are highly underestimated.  As for PSF colors, 
although there are still long tails that indicate the biases, at least the peak of the 
distributions are around zero now.  We adjust this sentence to make it more clear.

As for general comments for PSF photometry of highly blended stars.  Unfortunately we are 
not perfectly clear what causes this issue.  It is clearly related to the performace of 
debelnder in hscPipe, which is know to still have issue and is being improved now 
(please see Section 4.8 of Bosch+2017).  Given the depth of HSC survey, the situation for 
object deblending becomes much more tricky.  At this point, we have to leave this as a 
caveat.  PSF magnitude is still considered the best photometry for point sources, but we 
will remind the users to avoid using it for highly blended objects.  The text has been 
modified to reflect this point.

@@

----
10. the definition of highly blended

The referee is correct, that we should use consistent definition for highly blended
objects, which is b>0.05.  We have make it consistent across the draft.

---- 
11. Table 1, 2, 3, and 4

The statistical uncertainty is actually the standard deviation of (mag_output - mag_input)
within each input magnitude bin.  This is the what we used to describe "precision". 
For accuracy, we use the mean value of magnitude difference in each input magnitude bin.

All the captions of tables have been updated to make it more clear.

### 2017-09-13 draft/ms_v5.tex
All minor comments

    As for highly blended stars, Fig \ref{fig:psf_color} also shows that highly blended 
    stars have worse precision and accuracy in their colors compared to isolated stars. 
    At fixed input magnitude, the precision in $(g-i)$ is ${\sim}0.1$ mag worse for 
    highly blended stars.  
    Also, for blended stars, $(g-i)$ shows a bias towards bluer colors, while $(i-y)$ 
    shows a bias towards redder colors. 
    However, such biases appear to be less severe in terms of colors than in terms of
    PSF magnitudes.

@@

    Star--galaxy separation becomes increasingly difficult at faint magnitudes 
    ($i<24.0$ mag).
    In \hscpipe{}, the star--galaxy classification primarily depends on the 
    extendedness value, which is measured by the magnitude difference between PSF and 
    \cmodel{} photometry in $i$-band.
    For more details about this algorithm, please see \citet{Bosch2017}.

    Fig \ref{fig:sg} shows the current status of our star--galaxy classification 
    scheme.  
    Fig \ref{fig:sg} shows the difference between PSF and \cmodel{} magnitudes as a 
    function of input magnitude. 
    We find that $20$\% of synthetic stars at $i_{\mathrm{Input}}>23.0$ mag are 
    misclassified as extended objects, while only a tiny fraction of faint synthetic 
    galaxies ($i_{\mathrm{Input}}>24.0$) are misclassified as stars. 
    This confirms that the current star--galaxy classification strategy in \hscpipe{}
    results in a galaxy sample with \textbf{high completeness} and a star sample
    with \textbf{high purity}.

    It is also clear that the seeing condition strongly modifies the distributions
    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$. 
    Worse seeing condition makes star-galaxy separation more challenging. 
    The completeness and purity of galaxy and star samples at the faint end will 
    depend on seeing conditions.

    In the next data release, \hscpipe{} will include an improved star--galaxy 
    classifier which will be based on a machine learning method that takes both 
    size and color information into account.

@@

    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF magnitudes in all 
        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF magnitude and input 
        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:psf_mag}.
        Here, the precision is described using the statistical uncertainties of 
        $\Delta\mathrm{mag}$ within a series of input magnitude bins (\smag{}). 
        The accuracy of PSF photometry in the same magnitude bin is described by the 
        mean value of $\Delta\mathrm{mag}$.
        }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \rowcolor[gray]{.85} \multicolumn{6}{|c|}{\large{Table}: Summary of \forced{} PSF Colors} \\
    \hline \hline 
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 19.0 & \scolor{} &   0.023 &   0.022 &   0.018 &   0.019 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
    \hline 
    \rowcolor[gray]{1.0} 20.0 & \scolor{} &   0.028 &   0.024 &   0.019 &   0.019 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{.85} 21.0 & \scolor{} &   0.034 &   0.031 &   0.022 &   0.022 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.006 &   0.002 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{1.0} 22.0 & \scolor{} &   0.053 &   0.051 &   0.031 &   0.030 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.004 &   0.001 & \n0.004 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 23.0 & \scolor{} &   0.079 &   0.086 &   0.057 &   0.058 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.004 & \n0.015 & \n0.001 & \n0.004 \\
    \hline
    \rowcolor[gray]{1.0} 24.0 & \scolor{} &   0.116 &   0.122 &   0.111 &   0.112 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.015 & \n0.001 &   0.009 &   0.004 \\
    \hline
    \rowcolor[gray]{.85} 25.0 & \scolor{} &   0.162 &   0.185 &   0.192 &   0.216 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.044 & \n0.018 &   0.097 &   0.097 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF colors using $(g-i)$ and 
        $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} PSF color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:psf_color}.
        Here, we describe the precision and accuracy of PSF color measurements using 
        the statistical uncertainties and mean values of $\Delta\mathrm{Color}$ in 
        bins of input $i$ band magnitudes.
    }
        \label{tab:psfcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%

@@

    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} \cmodel{} magnitudes in all 
        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} \cmodel{} magnitude and input 
        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:cmodel_mag}.
        Other details are the same with Table \ref{tab:psfmag}.}
        \label{tab:cmodelmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 4 : CModel Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \rowcolor[gray]{.85} \multicolumn{6}{|c|}{\large{Table}: Summary of \forced{} \cmodel{} Colors} \\
    \hline \hline 
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 20.0 & \scolor{} &   0.068 & 0.051 &   0.072 &   0.046 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.013 & 0.002 & \n0.006 & \n0.001 \\
    \hline 
    \rowcolor[gray]{1.0} 21.0 & \scolor{} &   0.080 & 0.059 &   0.062 &   0.040 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.010 & 0.003 & \n0.003 & \n0.004 \\
    \hline
    \rowcolor[gray]{.85} 22.0 & \scolor{} &   0.089 & 0.072 &   0.071 &   0.059 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.002 & 0.002 & \n0.005 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 23.0 & \scolor{} &   0.105 & 0.090 &   0.109 &   0.103 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.018 & 0.001 & \n0.002 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 24.0 & \scolor{} &   0.136 & 0.127 &   0.175 &   0.170 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.008 & 0.006 &   0.012 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 25.0 & \scolor{} &   0.179 & 0.185 &   0.227 &   0.241 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.003 & 0.019 &   0.053 &   0.006 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} \cmodel{} colors using 
        $(g-i)$ and $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) 
        and \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics of 
        the difference between output \forced{} \cmodel{} color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:cmodel_color}.
        Other details are the same with Table \ref{tab:psfcolor}.
    }
        \label{tab:cmodelcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%

>>>>

    As for highly blended stars, Fig \ref{fig:psf_color} also shows that highly blended 
    stars have worse precision and accuracy in their colors compared to isolated stars. 
    At fixed input magnitude, the precision in $(g-i)$ is ${\sim}0.1$ mag worse for 
    highly blended stars.  
    \song{
    Unlike \psf{} magnitudes, where the distributions of magnitude differences 
    for highly--blended stars are clearly off, the distributions of \psf{} color 
    differences do peaks around zero.  
    Although the long asymmetric tails still indicate severe biases of \psf{} colors 
    for blended stars: $(g-i)$ color is clearly biased towards bluer colors, while 
    $(i-y)$ color shows bias towards redder values.
    The performances of \psf{} magnitude and color are still poor for highly-blended 
    stars in the current version of \hscpipe{}.  
    Object deblending becomes much more challenging at the depth of HSC SSP, and 
    the current deblending algorithm is known to have problems 
    (see Section~4.8 of \citealt{Bosch2017}) that could cause the problem here. 
    The deblending algorithm is also being constantly updated now, and we will keep 
    using \synpipe{} to evaluate its performance. 
    }

@@

    Star--galaxy separation becomes increasingly difficult at faint magnitudes 
    ($i<24.0$ mag).
    In \hscpipe{}, the star--galaxy classification primarily depends on the 
    extendedness value, which is measured by the magnitude difference between PSF and 
    \cmodel{} photometry in $i$-band.
    \song{
    Such method has its limitation and only works well down to $i\sim 24$ mag 
    (see Section 4.9.10 of \citealt{Bosch2017}).  
    For fainter extended objects, the difference between these two magnitudes become
    seeing- and model-dependent. 
    Moreover, right now, \hscpipe{} simply uses 
    $(m_{\mathrm{PSF}}-m_{\mathrm{CModel}})>0.0164$ mag to separate star and galaxies.  
    }

    Fig \ref{fig:sg} shows the current status of our star--galaxy classification 
    scheme.  
    Fig \ref{fig:sg} shows the difference between PSF and \cmodel{} magnitudes as a 
    function of input magnitude. 
    We find that $20$\% of synthetic stars at $i_{\mathrm{Input}}>23.0$ mag are 
    misclassified as extended objects, while only a tiny fraction of faint synthetic 
    galaxies ($i_{\mathrm{Input}}>24.0$) are misclassified as stars. 
    This confirms that the current star--galaxy classification strategy in \hscpipe{}
    results in a galaxy sample with \textbf{high completeness} and a star sample
    with \textbf{high purity}.
    It is also clear that the seeing condition strongly modifies the distributions
    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$. 
    Worse seeing condition makes star-galaxy separation more challenging. 
    The completeness and purity of galaxy and star samples at the faint end will 
    depend on seeing conditions. 
    \song{
    In \citet{HSCDR1}, the star--galaxy separation issue is tested in a small field 
    but under different seeing conditions and imaging depths (see their Section~5.7). 
    The overall conclusions are the same with ours, the efficiency and accuracy of 
    the current star--galaxy separation algorithm are reasonable at $i<23.0$ mag, but 
    depend on both seeing and depth.  
    We should point out that careful evaluation of star--galaxy separation algorithm 
    and the completeness of both types of objects are important to several scientific 
    topics of HSC SSP. 
    It deserve test at larger scale that covers different observational conditions and 
    with higher number density of objects. 
    It will be a major effort and is beyond the scope of this work.
    At the same time, \hscpipe{} will replace the current star--galaxy separation 
    algorithm with a much improved version that provides actual probability of being 
    star or galaxy (also see Section~4.9.10 in \citealt{Bosch2017}).  
    It will be available for the future data release, and will be tested by \synpipe{}. 
    }

@@

    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF magnitudes in all 
        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the statistics 
        \song{
        (standard deviation and mean value)
        }
        of the difference between output \forced{} 
        PSF magnitude and input value ($\Delta\mathrm{mag}$) shown in 
        Fig \ref{fig:psf_mag}.
        \song{
        Here, the precision is described using the \textbf{standard deviation} of 
        $\Delta\mathrm{mag}$ within a series of input magnitude bins (\smag{}). 
        The accuracy of PSF photometry in the same magnitude bin is described by the 
        \textbf{mean value} of $\Delta\mathrm{mag}$.
        }
        }
        \label{tab:psfmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 2 : PSF Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \rowcolor[gray]{.85} \multicolumn{6}{|c|}{\large{Table}: Summary of \forced{} PSF Colors} \\
    \hline \hline 
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 19.0 & \scolor{} &   0.023 &   0.022 &   0.018 &   0.019 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
    \hline 
    \rowcolor[gray]{1.0} 20.0 & \scolor{} &   0.028 &   0.024 &   0.019 &   0.019 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.007 &   0.003 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{.85} 21.0 & \scolor{} &   0.034 &   0.031 &   0.022 &   0.022 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.006 &   0.002 & \n0.004 & \n0.006 \\
    \hline
    \rowcolor[gray]{1.0} 22.0 & \scolor{} &   0.053 &   0.051 &   0.031 &   0.030 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.004 &   0.001 & \n0.004 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 23.0 & \scolor{} &   0.079 &   0.086 &   0.057 &   0.058 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.004 & \n0.015 & \n0.001 & \n0.004 \\
    \hline
    \rowcolor[gray]{1.0} 24.0 & \scolor{} &   0.116 &   0.122 &   0.111 &   0.112 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.015 & \n0.001 &   0.009 &   0.004 \\
    \hline
    \rowcolor[gray]{.85} 25.0 & \scolor{} &   0.162 &   0.185 &   0.192 &   0.216 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.044 & \n0.018 &   0.097 &   0.097 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} PSF colors using $(g-i)$ and 
        $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the 
        \song{
        standard deviation and mean value
        } 
        of the difference between output \forced{} PSF color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:psf_color}.
        Here, we describe the precision and accuracy of PSF color measurements using 
        the \song{standard deviation} and mean values of $\Delta\mathrm{Color}$ in 
        bins of input $i$ band magnitudes.
    }
        \label{tab:psfcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%

@@

    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} \cmodel{} magnitudes in all 
        five bands and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) and
        \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the 
        \song{
        standard deviation and mean value 
        }
        of the difference between output \forced{} \cmodel{} magnitude and input 
        value ($\Delta\mathrm{mag}$) shown in Fig \ref{fig:cmodel_mag}.
        Other details are the same with Table \ref{tab:psfmag}.}
        \label{tab:cmodelmag}
\end{table*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %%
% Table 4 : CModel Color
\begin{table}
    \begin{center}
    %% -------------------------------------------------------------------------------- %%
    \begin{tabular}{| c | c | c | c | c | c | }
    \hline
    \rowcolor[gray]{.85} \multicolumn{6}{|c|}{\large{Table}: Summary of \forced{} \cmodel{} Colors} \\
    \hline \hline 
    \multirow{2}{*}{$i_{\mathrm{Input}}$} & Color & \multicolumn{2}{|c|}{$(g-i)$} & \multicolumn{2}{|c|}{$(i-y)$} \\
    \cline{2-6}
      & FWHM & $0.45$\asec{} & $0.70$\asec{} & $0.45$\asec{} & $0.70$\asec{} \\
    \hline
    (mag) & & (mag) & (mag) & (mag) & (mag) \\
    \hline
    \rowcolor[gray]{.85} 20.0 & \scolor{} &   0.068 & 0.051 &   0.072 &   0.046 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.013 & 0.002 & \n0.006 & \n0.001 \\
    \hline 
    \rowcolor[gray]{1.0} 21.0 & \scolor{} &   0.080 & 0.059 &   0.062 &   0.040 \\
    \rowcolor[gray]{1.0}      & \mcolor{} &   0.010 & 0.003 & \n0.003 & \n0.004 \\
    \hline
    \rowcolor[gray]{.85} 22.0 & \scolor{} &   0.089 & 0.072 &   0.071 &   0.059 \\
    \rowcolor[gray]{.85}      & \mcolor{} &   0.002 & 0.002 & \n0.005 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 23.0 & \scolor{} &   0.105 & 0.090 &   0.109 &   0.103 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.018 & 0.001 & \n0.002 & \n0.005 \\
    \hline
    \rowcolor[gray]{.85} 24.0 & \scolor{} &   0.136 & 0.127 &   0.175 &   0.170 \\
    \rowcolor[gray]{.85}      & \mcolor{} & \n0.008 & 0.006 &   0.012 & \n0.007 \\
    \hline
    \rowcolor[gray]{1.0} 25.0 & \scolor{} &   0.179 & 0.185 &   0.227 &   0.241 \\
    \rowcolor[gray]{1.0}      & \mcolor{} & \n0.003 & 0.019 &   0.053 &   0.006 \\
    \hline
    \end{tabular}
    %% -------------------------------------------------------------------------------- %%
    \end{center}
    \caption{
        Summary of precisions and accuracies of \forced{} \cmodel{} colors using 
        $(g-i)$ and $(i-y)$ colors and in both \texttt{goodSeeing} (FWHM$=0.45$\asec{}) 
        and \texttt{badSeeing} (FWHM$=0.70$\asec{}) \tracts{} based on the 
        \song{
        standard deviation and mean value 
        }
        of the difference between output \forced{} \cmodel{} color and input value 
        ($\Delta\mathrm{Color}$) shown in Fig \ref{fig:cmodel_color}.
        Other details are the same with Table \ref{tab:psfcolor}.
    }
        \label{tab:cmodelcolor}
\end{table}
%% ------------------------------------------------------------------------------------ %%
